\chapter*{Acknowledgement}
\addcontentsline{toc}{chapter}{Acknowledgement}

 We would like to express our sincere gratitude to our project supervisor for providing us with continuous guidance and support throughout the development of this project. Without the supervisor's valuable suggestions and feedback, it would have been difficult for us to bring this project to its current state.

We are also thankful to the Department of Computer Engineering and all the faculty members who have supported us during this minor project. Their encouragement has helped us stay focused and motivated.

We would like to thank the Minor Project Coordinator, Krista Byanju, for organizing the mid-term defense and keeping us informed about the requirements and deadlines.

We also want to thank our friends and classmates who gave us feedback on the design and features of the application during its early stages. Their opinions helped us improve the overall idea of the project.

Finally, we are grateful to our families for their constant support and encouragement throughout this academic journey.


% \vspace{1.5cm}
% \noindent
% \begin{minipage}[t]{0.45\textwidth}
% \rule{5cm}{0.4pt}\\
% \textbf{Aayush Lohani}\\
% (BCT80004)
% \end{minipage}
% \hfill
% \begin{minipage}[t]{0.45\textwidth}
% \rule{5cm}{0.4pt}\\
% \textbf{Bimarsha Dahal}\\
% (BCT80026)
% \end{minipage}

% \vspace{1.5cm}
% \noindent
% \begin{minipage}[t]{0.45\textwidth}
% \rule{5cm}{0.4pt}\\
% \textbf{Gahan Raj Dangol}\\
% (BCT80033)
% \end{minipage}
% \hfill
% \begin{minipage}[t]{0.45\textwidth}
% \rule{5cm}{0.4pt}\\
% \textbf{Manish Poudel}\\
% (BCT80044)
% \end{minipage}
\clearpage
