\chapter{Introduction}
 
 \section{Background Theory}
 
In recent years, the increasing number of students and working professionals moving to new cities has created a growing need for platforms that help users find compatible roommates and build social connections. Existing social media and roommate-finding applications either lack compatibility-based matching or focus only on basic profiles, leaving a gap in the market.

TRIBAL is a cross-platform mobile application developed using Flutter and Django to address this problem. It enables users to create profiles, answer lifestyle-based onboarding questions, and find compatible roommates and activity partners through a weighted compatibility scoring algorithm. The application also supports event creation, participation, and real-time chat between matched users.

The weighted compatibility scoring approach was chosen over machine learning because it is transparent, easier to implement within the scope of a minor project, and provides meaningful matches based on users' preferences and interests.

 \section{Problem Statements}
People who want to find others with shared interests often have no proper platform to do so. General social media platforms are too broad and not designed for this kind of need. Activity-specific platforms like Meetup are not widely used in Nepal and do not support roommate finding at all.

The main problems that TRIBAL tries to address are:
\begin{itemize}
\item Finding compatible roommates and building a social circle is challenging for students and young professionals who move to new cities, as they often rely on informal methods such as friends or social media groups.


\item Existing platforms do not provide a single solution for roommate matching, activity partner discovery, and community building, while also overlooking important lifestyle compatibility factors.

\item TRIBAL addresses these challenges by offering a unified platform with compatibility-based roommate matching, activity partner discovery, event participation, and secure in-app chat.


\end{itemize}


TRIBAL aims to solve these problems by providing a single mobile platform where users can find compatible roommates, discover activity partners, join events, and chat with matches in a safe environment.

 \section{Objectives}
 The main objectives of this project are:
\begin{itemize}
  \item To design and develop a Flutter-based mobile application with a Django and PostgreSQL backend that enables users to find compatible roommates and activity partners through secure authentication, profile management, and a weighted compatibility matching algorithm.
  \item To implement core social features, including real-time chat, event creation and participation, and interest-based activity discovery, while ensuring secure communication and data management.
\end{itemize}

 \section{Scope and Applications}
 
The scope of this project as a minor project includes the following features:
\begin{itemize}


\item Develop a cross-platform Flutter application that enables users to find compatible roommates and activity partners through secure authentication, profile management, and preference-based matching.
\item Provide essential social features, including real-time chat, event creation and participation, and interest-based activity discovery to help users build meaningful connections.
\item Address the challenges of finding roommates and social networks, particularly for students and newcomers in Nepal, while serving as a scalable prototype for future enhancements such as verified profiles and location-based recommendations.

\end{itemize}

For the purpose of this minor project, the focus is on completing the core features
including the compatibility matching system, real-time chat, and event module. The
application is not intended for commercial deployment at this stage, but it demonstrates a
working prototype of the complete system.