\chapter{Epilogue}

\section{Tasks Completed}
So far, the team has completed the following tasks:
\begin{itemize}
\item UI design for onboarding, login, signup, and profile setup screens in Flutter.
\item Implementation of the three-slide onboarding screen with skip and next functionality.
\item Animated loading screen shown during navigation between major flows.
\item Django project setup with PostgreSQL as the database.
\item JWT-based authentication APIs for login and signup.
\item Database models for User and RoommateProfile.
\item Design of the roommate compatibility scoring algorithm with weighted factors and deal breaker rules.

\item Manual API testing using Postman.
\item GitHub repository setup for version control and team collaboration.
\end{itemize}

\section{Remaining Tasks}
The following tasks are still remaining and will be completed in the upcoming sprints before the final defense:
\begin{itemize}
\item Implementation of the scoring logic inside the roommate module (models, scoring, services, views, serializers, urls, admin).
\item Initial unit tests for the scoring function.
\item Integration of the roommate matching API with the Flutter frontend, so that real compatibility scores are shown in the app instead of placeholder data.

\item Implementation of the real-time chat system using Django Channels and WebSockets.
\item Chat screens in Flutter for one-to-one conversations between matched users.
\item Event creation and joining module, including event listing and filtering screens.
\item Notification system for new matches and messages.

\item Full integration testing between the Flutter frontend and the Django backend.
\item Final round of bug fixing and performance testing.
\item Preparation of the user manual and final project documentation.
\item Deployment of the backend and preparation for the final presentation.
\end{itemize}

\section{Updated Gantt Chart}
The original time schedule has been adjusted slightly based on the actual pace of development so far. The updated schedule below shows the completed sprints and the plan for the remaining weeks leading up to the final defense.


\begin{center}
\resizebox{1.0\textwidth}{!}{%
\begin{tabular}{|p{0.30\textwidth}*{7}{|p{0.035\textwidth}}|!{\color{red}\vrule width 1.5pt height 5pt depth 1pt}p{0.035\textwidth}*{4}{|p{0.035\textwidth}}|}
 \hline
 \textbf{Tasks} & \multicolumn{12}{c|}{\textbf{Weeks}} \\
 \hline
 & 2 & 4 & 6 & 8 & 10 & 12 & 14 & 16 & 18 & 20 & 22 & 24 \\
 \hline
Requirement Analysis \on{2}\off{10} \\
 \hline
System Design \off{2}\on{2}\off{8} \\
 \hline
Implementation \off{4}\on{4}\off{4} \\
 \hline
Testing and Evaluation \off{7}\on{3}\off{2} \\
 \hline
Deployment \off{10}\on{1}\off{1} \\
 \hline
Monitoring\off{11}\on{1} \\
 \hline
Documentation \on{12} \\
\hline
\end{tabular}}
\end{center}

The team is currently on Sprint 5. Based on the progress made so far, the team is confident that the remaining sprints can be completed within the original 16-week timeline, with some buffer time set aside before the final defense for bug fixing and documentation.
